Classless Java

### 2015-10-26 paper/sections/Formalization.tex
Little formalization and formatting improvements, also better explanations

\shadow{} choose the most specific version of a method, that is the unique version available, or a conflicted version from a set of possibilities.
We do not model overloading, so it is an error if multiple versions are available with different parameter types. Formally:\\*
\!\!\!\!$\begin{array}{ll}
\shadow(\m,\C_1\ldots\C_n)=\shadow(\methods)
& \mBody(\m,\C_i)\in\methods
\\ & \mif\ \mBody(\m,\C)\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\}
%\\ &\mor\ \mBody(\m,\C)=\mh\QM;
\\

\shadow()=\none\\
\shadow(\method)=\method\\
\shadow(\methods)=\Aux{mostSpecific}(\methods) &\mif\   \methods=\mh_1\QM;\ldots\mh_n\QM;\\
\shadow(\methods)=\conflicted\mh\QM;&\mif\ \Aux{mostSpecific}(\methods))\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\}\\
\Aux{mostSpecific}(\methods)=\method &
\mif\ \method \in \methods, \forall \method' \in \methods :  \method \subtype
                                       \method', \\
\T\ \m\oR\T_1\x_1\ldots \T_n\x_n\cR \subtype \T' \m\oR\T_1\x_1'\ldots\T_n\x_n'\cR & \mif\ \T\subtype \T'\\

\method \subtype
\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}=
\method\subtype\mh\QM;
\\
\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\subtype\method=
\mh\QM;\subtype\method
\end{array}$
Discuss about override\\*
\!\!\!\!$\begin{array}{ll}
\override(\none,\none)=\none\\
\override(\method,\none)=\method\\

\override(\none,\method)=\method &\mif\ \method\neq \conflicted\ \mh\QM;\\
\override(\method,\method')
=
\override(\method,\mh\QM;) & \method'\in\{\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}, \conflicted\ \mh\QM; \}\\
\override(\method,\mh')
=\method &\mif\ \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \}\\
& \mh\subtype\mh'
%\override(\_,\_)=\error & Otherwise
%\textsf{shadow}(body_1, body_2)=\emptyset & \textsf{if }body_1.\textsf{modifier}=body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_1 & \textsf{if }body_2=\emptyset\textsf{ or }body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_2 \hspace{.1in}  & \textsf{if }body_1=\emptyset\textsf{ or }body_1.\textsf{modifier}=\textbf{static}
\end{array}$

>>>>

\shadow{} choose the most specific version of a method, that is the unique version available, or a conflicted version from a set of possibilities.
We do not model overloading, so it is an error if multiple versions are available with different parameter types. Formally:\\*
\!\!\!\!$\begin{array}{l}
\shadow(\m,\C_1\ldots\C_n)=\shadow(\methods)
\whereNote
 \mwhere\ \mBody(\m,\C_i)\in\methods
\ \mif\ \mBody(\m,\C_i)\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\}
%\\ &\mor\ \mBody(\m,\C)=\mh\QM;
\\

\shadow()=\none\\
\shadow(\method)=\method\\
\shadow(\methods)=\Aux{mostSpecific}(\methods) 
\whereNote
\mwhere\   \methods\mbox{ is of the form }\mh_1\QM;\ldots\mh_n\QM;\\
\shadow(\methods)=\conflicted\mh\QM;
\whereNote
\mwhere\ \Aux{mostSpecific}(\methods))\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\}\\
\Aux{mostSpecific}(\methods)=\method
\whereNote
\mwhere\ \method \in \methods\ \mand\ \forall \method' \in \methods :  \method \subtype
                                       \method', \\
\T\ \m\oR\T_1\x_1\ldots \T_n\x_n\cR \subtype \T' \m\oR\T_1\x_1'\ldots\T_n\x_n'\cR
\whereNote
 \mwhere\ \T\subtype \T'\\

\method \subtype
\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}=
\method\subtype\mh\QM;
\\
\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\subtype\method=
\mh\QM;\subtype\method
\end{array}$
${}_{}$\\*
Where $\Aux{mostSpecific}$ return the most specific method using return type specialization as introduced in Java ??
We just check the subtype between method headers, so we discard information abut method implementation.\\*
${}_{}$\\*
The override function models how the implementation in an interface can override implementation in the superinterface; even in case of a conflict.
Note how we use the special value $\none$, and how (forth case) overriding can solve a conflict.
\\*
\!\!\!\!$\begin{array}{ll}
\override(\none,\none)=\none\\
\override(\method,\none)=\method\\

\override(\none,\method)=\method 
\whereNote
\mwhere\ \method\mbox{ not of the form } \conflicted\ \mh\QM;\\
\override(\method,\method')
=
\method 
\whereNote
\mwhere\ \method'\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}, \conflicted\ \mh\QM; \}\\
%\override(\method,\mh')
%=\method 
%\whereNote
%\mif\ \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \}, \mh\subtype\mh'
%\override(\_,\_)=\error & Otherwise
%\textsf{shadow}(body_1, body_2)=\emptyset & \textsf{if }body_1.\textsf{modifier}=body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_1 & \textsf{if }body_2=\emptyset\textsf{ or }body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_2 \hspace{.1in}  & \textsf{if }body_1=\emptyset\textsf{ or }body_1.\textsf{modifier}=\textbf{static}
\end{array}$
